Uncertainty Literature Review

### 2024-01-09 paper.qmd
added experiment paper checklist

# 4 LITERATURE SUMMARY

>>>>

# 4 LITERATURE SUMMARY
# Experiment paper checklist
General
- Specific Field of Research
- Question asked
- Risk or Uncertainty: 
- Noise vs signal (risk vs uncertainty)
- Major task goal
    - e.g. identify a bias or misunderstanding, compare two visualisation methods
- Minor task goal
    - Communication(value retrieval)
    - Analytical(complex consideration)
    - Exploration(free for all)

Uncertainty Considerations
	- Source
	- Level (statistical-ignorance)
	- Nature (Epistemic/Aleatory)

Visual Uncertainty taxonomy
- Explicit/implicit
    - (directly mapping or showing multiple outcomes)
- Intrinsic/Extrinsic 
    - (using existing symbols e.g. colour value, or new objects e.g. grids)
- Visually integral/separable 
    - (can or cannot be separated from the data) 
- Coincidence/adjacent 
    - (if data and uncertainty are in integrated or separate views
- Static/dynamic 
    - (animation/interaction)

Other plot considerations
	- Dimension of data
	- Dimension of uncertainty
	- Feature mappings

Extra (not necessarily recorded)
	- Metrics used (and recorded)
	- Possible Heuristics
	- What is the ground truth?
	- Participant literacy
